\documentclass[10pt,a4paper]{article}
\usepackage[a4paper, left=1.5cm, top=1cm, right=1.5cm, bottom=1.5cm]{geometry}
\usepackage{layout}
\usepackage{sectsty}
\usepackage{titlesec}
\usepackage{MnSymbol,wasysym}
\usepackage{graphicx,txfonts}

\newcommand{\heart}{\ensuremath\varheartsuit}

\setcounter{secnumdepth}{0}

\sectionfont{\fontsize{12}{14}\selectfont}

\titlespacing\section{0pt}{10pt plus 0pt minus 0pt}{0pt plus 0pt minus 10pt}

\begin{document}

\noindent \textbf{The Cover Letter}

\vspace{3cm}

\noindent To: \textbf{Reddit Inc.} \\
For the job role: \textbf{Senior Software Engineer, Crypto Security} \\ \\

\noindent Hello, \\ \\

\noindent I just found your job post on LinkedIn. I've using been using Solidity for the past two years working on some of the current tokens available in the market; ARTEQ and QLINDO. Throughout these years, I learned a lot about EVM internals and how security can be guaranteed for smart contracts. I have strong background in information and network security and have been part of a CERT center back in Iran. \\ \\

\noindent I have also used various Solidity patterns like Proxy Pattern in order to make a big Solidity code modular and maintainable. My contracts have also gone through various auditing processes mainly by Certik. So, I'm familiar with the known issues when it comes to developing a secure smart contract. \\ \\

\noindent In parallel, as a Senior Software Engineer, I do have strong hands-on C/C++, Golang, NodeJS, and Rust. As a cloud engineer, I have been dealing with Kubernetes deployments using AWS EKS technology. As a distributed systems architect, I have been actively working with architects and the product team in order to translate complex distributed problems into technical tasks. \\ \\

\noindent I am also a book author. My latest book, Extreme C, is about the advanced usage of C language in modern software development. \\ \\

\noindent I'm looking forward to hearing from you. \\ \\

\noindent Best regards, \\
\noindent Kam

\end{document}
