\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[margin=1.0 in]{geometry}
\usepackage{longtable}
\usepackage[linewidth=1pt]{mdframed}

\newif\ifanswers
\answerstrue

\setlength{\LTleft}{-0.5in}

%\setcounter{secnumdepth}{-1} 

\begin{document}
\title{Curriculum Vitae}
\author{Kamran Amini}
\maketitle

\section{Overall Information}

	\small \textbf{Personal Information} \\
			\indent Name : Kamran \\
			\indent Family : Amini \\
			\indent Birth date : 1987 Apr 25 \\
			\indent Birth place : Tehran, Tehran, Iran \\
			\indent Nationality : Iranian \\
			\indent Current living place : Tehran, Tehran, Iran \\
			\\
	\small \textbf{Contact Information} \\
			\indent Phone : 
			\indent \indent \texttt{+98 21-33436149} \\
			\indent Mobile : 
			\indent\indent \texttt{+98 935-45-92-365} \\
			\indent	Email :  
			\indent \indent \texttt{amini.k@cert.sharif.edu} \\ 
			\indent GMail :
			\indent \indent \texttt{kamran.amini.eng@gmail.com} \\
			\indent Home Address : \\ \indent \indent No.12, Mahzoon Alley, Tayeb St., Khorasan Sq., Tehran, Tehran, Iran \\
			\\
	\small \textbf{Current Employment} \\
			\indent Company : SharifCERT at Sharif University of Technology, Tehran, Tehran, Iran \\
			\indent Webstie : \texttt{https://cert.sharif.edu/?lang=en} \\
			\indent Since : 2011 December \\
			\\					
	\small \textbf{ Educational Information} \\
			\indent - High school Diploma in Mathematical Sciences, Sanie-far High school, Finished at 2005 with GPA 19/20 \\
			\indent - Studied Bachelor in Software Engineering, University of Isfahan, started at 2005 September and left at 2008 September with 99 completed course units out of 141 course units and GPA 14.28/20 \\
			\\
	\small \textbf{Speaking languages} \\
			 \indent Persian : Native \\
			 \indent English : Fluent \\
			 \indent Japanese : Lower Intermediate, Studying for JLPT N1 \\
			 \indent Dutch : Beginner \\
			 \\
	\small \textbf{Hobbies and Interests} \\
		     \indent Music(Rock, Metal, Heavy Metal, Doom Metal, Progressive Metal, etc) \\
         	 \indent Mathematics(Abstract Algebra, Probabilities, etc) \\
	         \indent Physics(Quantum Mechanics, Particle Physics, etc) \\
	         \indent Cryptography(Quantum Cryptography) \\
	         \indent Musicology and playing musical instruments \\
	         \indent Japan, Japanese Language, Japanese Animes, Japanese Horror Movies \\ \\ \\ \\
  
\begin{mdframed}[leftmargin=10pt,rightmargin=10pt]      
\section{Activities as an Instructor}
		\begin{itemize}
			\item \textbf{Mojtama E Fanni E Tehran,MFT(2011 to present) at Tehran, Iran}
				\begin{itemize}
					\item Algorithms and Object Oriented Programming
					\item Basic and Advanced Java Programming (J2SE)
					\item MCTS: Microsoft C\#.NET(.NET Framework Foundation and Framework Design)
					\item MCTS: Microsoft SQL Server 2008(Design, Maintenance and Administration)
				\end{itemize}
			\item \textbf{Novin Parsian Master Educational Institute(2009 to 2011) at Tehran, Iran}
				\begin{itemize}
					\item MCTS: Microsoft C\#.NET Programming					
					\item Microsoft SQL Server 2005, 2008 Design and Administration
					\item Oracle 10g Design and Administration
					\item Object Oriented Programming using Java
				\end{itemize}
			\item \textbf{Padideh Educational Institute(2006 to 2009) at Tehran, Iran}
				\begin{itemize}
					\item Software related academic courses e.g Algorithms, Data Structure, Algorithm Design, etc.
					\item Payam Noor University Master Degree, Database Systems(Based on C.J.Date book)
				\end{itemize}
			\item \textbf{Iran Khodro Co.}
				\begin{itemize}
					\item SeptaNSF Framework as the Consultant Specialist and Architect from Septa Co.
				\end{itemize}
		\end{itemize}
\end{mdframed}

\clearpage

\begin{mdframed}[leftmargin=10pt,rightmargin=10pt]
\section{Topics willing to teach}
	\begin{itemize}
		\item Making Java Applications using J2SE (Basic and Advanced)
		\item Java Web Programming (J2EE)
		\item Java Network Programming (L2 and L3)
		\item Java Secure Coding (Based on Oracle Java Secure Coding topics)
		\item Spring Framework (IoC, Web Framework, Security, etc)
		\item Oracle Database Design and Administration
		\item Linux (Basic and Administration)
		\item C/C++ Programming in both Linux and Windows (gcc, g++, MinGW, VC6, etc)
		\item C/C++ Secure Coding
		\item MCTS .NET courses (Windows Forms, ASP.NET, SQL Server, etc)
		\item Computer Courses (Algorithms, Data Structure, Algorithm Design, etc)
	\end{itemize}
	
\end{mdframed}


\section{Professional Career as Software Developer/Designer}
	\begin{itemize}
		\item \textbf{Aramin IT Co. (2008 March -2009 June) at Isfahan, Iran}
			\begin{itemize}
				\item \small \textbf{Isfahan Province Electricity Distribution Center, 121 Call Center} \\					
				This was a set of projects using VC++ and C\#.NET which was responsible for call handling and redirecting in Isfahan Electricity Distribution Center. This consisted of a C++ service which was written to control and monitor a Panasonic TD 200 call center. It was using TAPI API to control the call center. Also, there were some desktop applications written in C\#.NET which they were used by call center agents and managers to monitor, accept, reject, redirect and perform other operations on the calls. DBMS used for this project was Micrsoft SQL Server 2005. This application were designed by me and one of my co-workers.
			\end{itemize}
		\item \textbf{Shabakeh Pardaz Rayaneh Co. (2009 June-2009 September) at Isfahan, Iran}
			\begin{itemize}
				\item \small \textbf{Isfahan Province Electricity Distribution Center, 121 Call Center} \\
				This was the same project at previous company, Aramin IT, which was transferred to this company and I had to move to this company to work on project again. \\
				\item \small \textbf{Recording and Archiving System at Isfahan Central Jails Organization} \\
				The recording system wasn't developed by us. The archiving system was implemented using C\#.NET and Microsoft SQL Server 2005. Many database related issues like Heavy loads and load balancing, Partitioning, Indexes, etc were encountered. Software design was mine. 
			\end{itemize}
		\item \textbf{Septa Co. (2009 September-2011 August) at Tehran, Iran}
			\begin{itemize}
				\item We used Microsoft Visual Studio 2008 alongside Microsoft Visual Source Safe 2005 for code development.
				\item \small \textbf{SeptaNSF; A .NET based Framework} \\
				This was a .NET based framework implemented for internal usages and later become a product. It also had a code generator which was able to generate Business Logic Layer entities and their adapters. it was entirely written in C\#.NET 3.5 and I was one of its developers and designers. WCF related namespaces and classes like base proxies, base services and different bindings were developed by me. \\
				\item \small \textbf{\texttt{www.1st.ir} B2B Portal} \\
				It was one of the first Iranian Business 2 Business portals. Written in ASP.NET C\#.NET 3.5 over a Microsoft SQL Server 2008 R2 database. All parts relating to WCF web services were developed by me. Also, portal integration with other products using web services were done by me. \\
				\item \small \textbf{PayamGostar Application} \\
				A business directory desktop application written entirely in C\#.NET 3.5 on a Microsoft SQL Server 2008 R2 database. It allowed people to search, save and edit their customers and a bank of businesses called business directory. Also it was checking user's activation status using WCF web services from www.1st.ir portal over a HTTPS channel. In addition, new businesses could be synchronized with \texttt{www.1st.ir} portal using WCF web services. \\
				\item \small \textbf{Septa Update Center} \\
				An update/patch system integrated with development procedures to provide updates for company's products. It was entirely written in C\#.NET 3.5. An updater service with a desktop updater application were given to clients for updating their product instances. It was fully designed and implemented by me and now it is working as the main update/patch package for Septa Co. products. It uses SOA architecture and implemented using WCF services for downloading patches, updates, checking activation and subscription and deactivating product instances. \\
				\item \small \textbf{Septa Automation System} \\
				It was an internal ASP.NET C\#.NET 3.5 website for entrance system, salary calculations, product instances, serial code generation, tracking sold products, etc. It was all implemented by me. It was using ASP.NET membership bundle as its authentication component.
			\end{itemize}
		\item \textbf{Gostaresh Faryanad Sharif Co.; SEPDCo. (2011 October to 2012 June) at Tehran, Iran}
			\begin{itemize}
				\item \small \textbf{SEPDCo Gas Network Simulator System} \\
				 A gas network and pipeline designer and simulator application written entirely in C++ using Qt framework. I was developer for the desktop application which was written in C++ and Qt View Framework. I used Qt View Framework classes like QWidget, QMainWindow, QGraphicsScene, QGraphicsView and signals, slots and all needed concepts in Qt. The application had no database and everything was serialized using XML or Binary Serializers. We were using Microsoft Visual Studio 2008 for developing the project. \\
			\end{itemize}
		\item \textbf{Sharif CERT(APA Sharif) (2011 December to present) at Tehran, Iran} \\ \\
		 NOTICE : Projects and their details are confidential and I can't mention them. So, a general overview on technologies will be given.
			\begin{itemize}
				\item Network security implementation using Java, C and C++ under Linux environments
				\item Using SVN and Git alongside Eclipse IDE
				\item Research and develop on L2 and L3 security issues
				\item Working with algorithms and data structures which are involved in security related domains. 
				\item Malware analysis, Traffic analysis, Attack analysis
				\item 2012 May, Member of Technical Team, CTF Competitions, Iran's Second National Hacking Contest, Sharif University of Technology. Java Secure Coding Question Designer and Auditor.
			\end{itemize}
	\end{itemize}
	
\section{Worked Projects}
			These are a list of major projects which I've done or participated in my professional career. They can be defined whether by companies or by myself. Each project has an index which can be used for reading the following table.
			
			\begingroup
			\footnotesize
			\begin{longtable}{ c c c c c c }
			\caption{Worked Projects}
			\label{table:nolin}
			\tabularnewline
				\hline
				Project Index & Languages & DBMS & Roles & Libraries\\
				\hline
				1 & C++,C\#.NET & SQL Server & Developer, Designer & TAPI 2.0 \\
				2 & C\#.NET & SQL Server & Developer, Designer & - \\
				3 & C\#.NET & - & Developer, Designer \\
				4 & C\#.NET & SQL Server & Developer & WCF Services, ASP.NET \\
				5 & C\#.NET & SQL Server & Developer, Designer & WCF Services, Interop \\
				6 & C\#.NET & SQL Server & Developer, Designer & WCF Services, Compression \\
				7 & C\#.NET & SQL Server & Developer, Designer & ASP.NET \\
				8 & C++ & - & Developer, Designer & Qt Framework \\
				9 & C++ & - & Idea Owner, Developer and Designer & \\
				10 & Perl & - & Idea Owner, Developer and Designer & \\
				11 & C++ & MongoDB & Idea Owner, Developer and Designer & Qt, Boost \\
				12 & Java,C,C++ & PostgreSQL & Developer, Designer & libpcap, J2EE, Qt \\
				\hline
			\end{longtable}
			\endgroup

		 	 1: Isfahan Province Electricity Distribution Center, 121 Call Center \\
			 2: Recording and Archiving System at Isfahan Central Jails Organization \\ 
			 3: SeptaNSF; A .NET based Framework \\
			 4: 1st.ir B2B Portal \\
			 5: PayamGostar Application \\
			 6: Septa Update Center \\
			 7: Septa Automation System \\
			 8: SEPDCo Gas Network Simulator System \\
			 9: ImgProcLib; A C++ Image Processing Library \\
			10: OpenPerl::MVC web framework \\
		    11: MafiaClub; An online multiplayer game \\
			12: SharifCERT projects \\
			\\

\section{Expertise}
	\subsection{Source Version Control systems}
		\begin{itemize}
			\item SVN
			\item Git
			\item Microsoft Visual Source Safe 2005
			\item Microsoft Team Foundation System
		\end{itemize}
	\subsection{Programming and Scripting languages}
		\begin{itemize}
			\item \textbf{C, C++}
				\begin{itemize}
					\item I've started using C++ since high school in a 2D Soccer Simulation Robocup team.
					\item I've worked with \texttt{gcc} and \texttt{g++} in Linux based operating systems like Fedora and Ubuntu.
					\item I've written some projects with Visual C++ using MS Visual Studio 6.0 and 2008 in Windows environments. I've used C++ CLI too but I prefer standard C++.
					\item I've worked with \texttt{boost} and \texttt{Qt} frameworks alongside \texttt{STL} in various projects.
					\item Also I have done some windows desktop applications using Visual C++ 6.0 and above.
					\item C++ secure coding according to CERT C++ Secure Coding.
				\end{itemize}
			\item \textbf{Java}
				\begin{itemize}
					\item It is since 2012 which I've started Java seriously as a major part of my career. I was familiar with Java since high school but the professional career has been started since I joined Sharif CERT.
					\item Most of my projects were written using J2SE framework but I have some experiences about using JBoss as a J2EE Application Server while using HornetQ. So I'm a bit familiar with J2EE Architecture.
					\item Currently, studying Spring framework and its Web MVC framework. Also, as a security solution I'm studying Spring Security framework for securing web application written using Spring Web MVC framework. Current studying is because of a project which should be written in pure Spring.
					\item All of my projects have been written in Ubuntu using Eclipse IDE.
					\item Most of the projects were server side and they had to be written very carefully. They had to work under heavy loads, they had to respond to many requests in a little fraction of time and most of them were 24/7 services.
					\item I've worked with \texttt{java} and \texttt{javac} as Java command line launcher and compiler.
					\item Java secure coding according to The CERT Oracle Secure Coding for Java.
				\end{itemize}
			\item \textbf{C\#.NET}
				\begin{itemize}
					\item I've written several applications using C\#.NET 3.5 both Windows Form and Web applications.
					\item I've written some projects using C\#.NET 4 but I'm more experienced in C\#.NET 3.5.
				\end{itemize}
			\item \textbf{Perl} 
				\begin{itemize}
					\item It is since 2011 which I have started programming with Perl. I've worked with 5.8 and 5.14 versions.
					\item I've used Perl to write an Apache module. Then it became a web MVC framework called OpenPerl::MVC. It is not completed yet but once it gets ready I'm going to publish it on CPAN archive.
				\end{itemize}
			\item \textbf{PHP}
				\begin{itemize}
					\item I've done some websites using PHP but all of them were for testing purposes. Honestly, this was my first server-side programming language and I changed it to Perl on Linux environments. I've used PHP alongside with MySQL as its RDBMS.
				\end{itemize}
			\item \textbf{Unix/Linux Shell}
				\begin{itemize}
					\item I do all of my OS related jobs using shell scripts under Linux environments. Installers, Preparation packages, Folder layout makers and many more jobs can be done using shell scripts. I use them heavily while I'm working on a project. They are great alongside Perl scripts and give you a lot of power to automate and centralize system routines.
				\end{itemize}
		\end{itemize}
		
	\subsection{Operating Systems}
		\begin{itemize}
			\item \textbf{Ubuntu,Debian}
				\begin{itemize}
					\item Version 10.x and 11.x
					\item Programming with C, C++ and Java
					\item Shell Programming
					\item Socket programming
					\item Kernel module programming
					\item Character devices programming
					\item Highly loaded daemons using Java and C++
				\end{itemize}
			\item \textbf{CentOS,Fedora}
				\begin{itemize}
					\item Version 5.x and 6.x
					\item Programming with C++ and Perl
					\item Shell Programming
					\item Socket programming
					\item Web applications using Perl
				\end{itemize}
			\item \textbf{FreeBSD}
				\begin{itemize}
					\item Version 8.4
					\item Programming with C
					\item Kernel module programming
					\item Character devices programming
					\item Socket programming
				\end{itemize}
			\item \textbf{Microsoft Windows}
				\begin{itemize}
					\item XP, Vista and 7
					\item Programming with C++ and C\#.NET
				\end{itemize}
		\end{itemize}
		
	\subsection{Database Systems}
		\begin{itemize}
			\item \textbf{PostgreSQL}
				\begin{itemize}
					\item PostgresSQL 8.4 under Ubuntu and Debian environments
					\item Configuring database engine using configuration files like pg\_hba.conf, etc.
					\item Used as data source for Hibernate framework in Java projects.
					\item Used \texttt{psql} client admin tool alongside shell scripts to automate database installation steps.
				\end{itemize}
			\item \textbf{Microsoft SQL Server}
				\begin{itemize}
					\item 2005 and 2008 Versions
					\item Database design and Implementation
					\item I've taught Microsoft SQL Server 2008 Design and Administration for 2 years based on MCTS Standard.
				\end{itemize}
			\item \textbf{MongoDB}
				\begin{itemize}
					\item Version 2.0.5
					\item Recently I've started a project which uses MongoDB as its noSQL and document oriented database management system.
					\item I've used MongoDB C\# wrapper which allows you to use MongoDB in C\#.NET projects. Also have used its C++ driver and wrapper which is MongoDB's first default wrapper.
				\end{itemize}
			\item \textbf{Oracle}
				\begin{itemize}
					\item Oracle 10g and 11g
					\item Database design
					\item A little experience about administration. I've taught some courses related to Oracle Database Design and Administration.
				\end{itemize}
		\end{itemize}
	
	\subsection{APIs and Frameworks}
		\begin{itemize}
			\item \textbf{Telephony API} 
				\begin{itemize}
					\item TAPI 2.0 and TAPI 3.0
					\item Used with C, C++ and C\#.NET
					\item Programming with WAPI (Wave API) alongside TAPI for voice recording and IVR(Interactive Voice Response) systems
					\item Familiar with JTAPI (Java Telephony API)
				\end{itemize}
			\item \textbf{Packet Capturing}
				\begin{itemize}
					\item libpcap with C++ in Ubuntu distribution
					\item JNetPcap, a Java wrapper for libpcap, in Ubuntu distribution
					\item Used in applications for Network Traffic and Packet Flow analysis
				\end{itemize}
			\item \textbf{Qt C++ Framework}
				\begin{itemize}
					\item Used Qt data structural and common classes like \texttt{QList}, \texttt{QMap}, etc
					\item Socket programming
					\item GUI programming, worked with \texttt{QWidget} objects, Signals, Slots, etc
				\end{itemize}
			\item \textbf{Boost C++ Framework}
				\begin{itemize}
					\item Familiar with data structural and common classes
				\end{itemize}
			\item \textbf{O/R Mappers}
				\begin{itemize}
					\item LLBLGen
					\item Microsoft Entity Framework
					\item Hibernate for Java(Specifically with PostgreSQL)
				\end{itemize}
			\item \textbf{Windows Communication Foundation(WCF)}
				\begin{itemize}
					\item Transport and Message security models
					\item IIS Hosting and Windows Service Hosting
					\item Basic and WS bindings, Custom bindings
				\end{itemize}
			\item \textbf{Microsoft Hooking framework}
				\begin{itemize}
					\item Dll injection
					\item Writing hooks for monitoring and redirecting Windows Calls.
				\end{itemize}
		\end{itemize}		

		 
\section{Scientific Career}
	\subsection{Interests}
		\begin{itemize}
			\item Information Theory, Cryptography, Quantum Cryptography
			\item High Performance Computing
		\end{itemize}
	\subsection{Memberships}
		\begin{itemize}
			\item 2012 May, Member of Technical Team, CTF Competitions, Iran's Second National Hacking Contest, Sharif University of Technology. Java Secure Coding Question Designer and Auditor.
		\end{itemize}
	\subsection{Publications}
		\begin{itemize}
			\item Working on an article for 'The 19th IEEE International Symposium on High Performance Computer Architecture'. The article suggests a HPC-Architecture for Clustered Cloud environments.
		\end{itemize}
	\subsection{Co-author}
		\begin{itemize}
			\item 2007 Co-author for Master Thesis "Pattern Recognition using Feature Extraction for R6 robots.", Islamic Azad University, Science and Research
			\item 2010 Co-author for Master Thesis "Author Verification using Letter Features in Persian Alphabet", Tarbiat Modares University
			\item 2013 Working as co-author on a Master Thesis about Quantum Cryptography, Islamic Azad University, Science and Research
		\end{itemize}
		
\end{document}